### 2017-08-22 paper/incomeShocks-jde-r1.tex
Add results with interaction with assets to appendix

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{The Effects of Crop Loss on Contraceptives Use by Assets}
\label{tab:assets}
\begin{tabular}{@{} l D{.}{.}{1.5} D{.}{.}{1.5}  D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5}  @{}}
\toprule
                                                       & \mco{}              &\mco{}               &\multicolumn{3}{c}{Contraceptive Use}\\ \cmidrule(lr){4-6}
                                                       & \mco{Pregnant}      &\mco{Childbirth}     &\mco{Any}            &\mco{Traditional}    & \mco{Modern}        \\ \midrule
Crop loss - 1-7 months (200 TZS or above)              &      -0.095\sym{**} &                     &       0.093\sym{**} &       0.065\sym{**} &       0.021         \\
                                                       &     (0.045)         &                     &     (0.037)         &     (0.032)         &     (0.015)         \\
Crop loss - 1-7 months                                 &       0.000         &                     &      -0.003         &      -0.001         &      -0.002         \\
\hs \X initial assets (10,000 TZS)                     &     (0.001)         &                     &     (0.003)         &     (0.003)         &     (0.002)         \\
Crop loss - 7-14 months (200 TZS or above)             &                     &      -0.164\sym{***}&                     &                     &                     \\
                                                       &                     &     (0.053)         &                     &                     &                     \\
Crop loss - 7-14 months                                &                     &       0.001         &                     &                     &                     \\
\hs \X initial assets (10,000 TZS)                     &                     &     (0.002)         &                     &                     &                     \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{741}        &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

>>>>

% Effects of Crop Loss on Contraceptives Use by Assets
\input{../tables/appendix_asset_interaction.tex}
